ManuscriptGAM

### 2024-03-15 Code/Plots_GAM.Rmd
changed how plots are generated and saved such that 'run all' is used instead of changing strain name in the chunk that generates and saves plots. Prone to errors.

# Plot red light GAM, must change GAMStrain and rerun chunk to generate plot of each strain
``` {r GAM Plot Red WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Red" 
WL_nm = 660 
PlotWL <- "deltaOD"

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         # PhotoperiodLabel = "Photoperiod",

         OxygenLabel = "Oxygen Concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
     xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    # labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
    theme_classic() +
    theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    # labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
  theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "A", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    # labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) +  #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))# change to 25 and 30 for thesis
          # axis.title.y = element_blank()))

                   # ,  left = textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", rot = 90, vjust = 0.5, hjust = 0.45, gp=gpar(fontsize=30)), bottom = textGrob("Photoperiod (h)", gp=gpar(fontsize=20), vjust = 0.2, hjust = 0.6))

#  for thesis
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 10, width = 6 )

# for presentation
  # ggsave(file = file.path(paste(PlotsPath, sep = "/"), paste(Project, "Hypervolume_GAM", GamColor, GamStrain, "Oxy", ".png", sep = "_"), fsep = .Platform$file.sep), plot = p3_Red,  height = 7.6, width = 6)

@@

# Plot blue light GAM, must change GAMStrain and rerun chunk to generate plot for each strain
``` {r GAM Plot Blue WL}
GamStrain = "MIT9313" # MIT9313 MED4 SS120
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

@@

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(

         # PhotoperiodLabel = "Photoperiod",

         OxygenLabel = "Oxygen Concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

@@

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "C", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    # labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
   theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         #DM == "Chl",
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    #labs(title = paste("Upper 10% Lmu", GamWL, Proxy, PlotStrain)) + 
    #geom_text(x = 4, y = 200, label = "B", size = 5) +
    xlab(NULL)+
     # xlab("Photoperiod (h)") +
      ylab(NULL)+
    # ylab("PAR (µmol photons"~ m^-2~ ~s^-1~ ")") +
    # ggh4x::facet_nested(cols = vars(OxygenLabel, O2_uM),
    #                     labeller = labeller(O2_uM = label_value, OxygenLabel = label_value)) +
    #facet_grid(cols = vars(O2_uM)) +
    # labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
  theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

@@

p3_Blue <- grid.arrange(
                         ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                         legend1, 
                        legend2, 
                        legend3, 
                        layout_matrix = LayoutNiche)

>>>>

@@

# Plot red light GAM for MED4
``` {r MED4GAM Plot Red WL}
GamStrain = "MED4" 
GamColor = "Red" 
WL_nm = 660 
PlotWL <- "deltaOD"

@@

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         OxygenLabel = "Oxygen concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

@@

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
     xlab(NULL)+
      ylab(NULL)+
    theme_classic() +
    theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
   theme_classic() +
  theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))

HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
    #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

# comment rows that are not included in grid arrange 
LayoutNiche <- rbind(
                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2 plotted
                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2 plotted
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(1, 1, 1, 1, 4),   # For 250 uM O2
                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                     )

p3_Red <- grid.arrange(
                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment if want 2.5 uM O2 plotted
                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                         theme(legend.position = 'none'), 
                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                         theme(legend.position = 'none'),
                       # legend1,   # remove comment if want 2.5 uM O2 plotted
                        legend2, 
                        legend3, 
                       layout_matrix = LayoutNiche)

# Plot blue light GAM for MED4
``` {r MED4GAM Plot Blue WL}
GamStrain = "MED4" 
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         OxygenLabel = "Oxygen concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
   theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+ 
  theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

# comment rows that are not included in grid arrange 
LayoutNiche <- rbind(
                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2   # remove comment if want 2.5 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(1, 1, 1, 1, 4),   # For 250 uM O2
                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                     )

p3_Blue <- grid.arrange(
                         # ContourLowO2 +   labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),  
                        ContourIntO2 +  labs(title = bquote("D.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourHighO2 + labs(title = bquote("C.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
                        # legend1,    # remove comment if want 2.5 uM O2
                        legend2, 
                        legend3, 
                        layout_matrix = LayoutNiche)

```{r combine red and blue light MED4GAM plots}

# add titles to plot
LabelledCombinedGam <- grid.arrange(arrangeGrob(CombinedGAM, left = y.grob, bottom = x.grob))

```{r save MED4GAM plots}
# MED4GAM,png for manuscript
 ggsave(file = file.path(paste(PlotsOut, sep = "/"), paste(GamStrain, "GAM", ".png", sep = ""), fsep = .Platform$file.sep), plot = LabelledCombinedGam,  height = 10, width = 10)

# MED4GAM is Fig4.tiff for PLOSONE submission
 ggsave(file = file.path(PlotsOutPLOS, "Fig4.tiff", fsep = .Platform$file.sep), plot = LabelledCombinedGam, device = NULL, scale = 1,  height = 10, width = 10, compression = "lzw")

# Plot red light GAM for SS120
``` {r SS120GAM Plot Red WL}
GamStrain = "SS120" 
GamColor = "Red" 
WL_nm = 660 
PlotWL <- "deltaOD"

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         OxygenLabel = "Oxygen concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
     xlab(NULL)+
    theme_classic() +
    theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
  scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
   theme_classic() +
  theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=23)))

HyperChlPlotHigh <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "250"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "250") 
ContourLines <- ContourLines$quantileValue

(ContourHighO2 <- ggplot(na.omit(HyperChlPlotHigh), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c("white", ColourDF), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+ #https://stackoverflow.com/questions/15074127/use-expression-with-a-variable-r
    theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

# comment rows that are not included in grid arrange 
LayoutNiche <- rbind(
                      # c(3, 3, 3, 3, 6), # For 2.5 uM O2     # remove comment if want 2.5 uM O2
                     # c(3, 3, 3, 3, 6), # For 2.5 uM O2    # remove comment if want 2.5 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(2, 2, 2, 2, 5),   # For 25 uM O2
                     c(1, 1, 1, 1, 4),   # For 250 uM O2
                     c(1, 1, 1, 1, 4)    # For 250 uM O2
                     )

p3_Red <- grid.arrange(
                       # ContourLowO2 +   labs(title = bquote("C.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) + theme(legend.position = 'none'),   # remove comment for MIT9313
                       ContourIntO2 + labs(title = bquote("B.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                         theme(legend.position = 'none'), 
                       ContourHighO2 + labs(title = bquote("A.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                         theme(legend.position = 'none'),
                       # legend1,   # remove comment if want 2.5 uM O2
                        legend2, 
                        legend3, 
                       layout_matrix = LayoutNiche)

# Plot blue light SS120GAM
``` {r GAM Plot Blue WL}
GamStrain = "SS120"
GamColor = "Blue"
WL_nm = 450 
PlotWL <- "deltaOD"

PicoGAM_Plot_Prep <- PicoGAM_Pred %>%
  filter(Wavelength %in% PlotWL,
         Strain %in% GamStrain,
         WL %in% WL_nm) %>%
  mutate(
         OxygenLabel = "Oxygen concentration (uM)",
         O2_level = case_when(O2_uM == 2.5 ~ "low",
                              O2_uM == 25 ~ "intermediate",
                              O2_uM == 250 ~ "high"),
         Color_name = case_when(WL == "450" ~ 'Blue',
                                WL == "530" ~ 'Green',
                                WL == "660" ~ 'Red',
                                WL == "WW" ~ 'White')) %>%
  unite(WL_O2, Color_name, O2_level, sep = "_", remove = FALSE)

HyperChlPlotLow <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "2.5"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "2.5") 
ContourLines <- ContourLines$quantileValue

(ContourLowO2 <- ggplot(na.omit(HyperChlPlotLow), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
   theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

HyperChlPlotInt <- PicoGAM_Plot_Prep %>%
  filter(
         Strain %in% GamStrain,
         Wavelength %in% PlotWL,
         O2_uM == "25"
  )
ContourLines <- ContourBreaks %>%
  filter(O2_uM == "25") 
ContourLines <- ContourLines$quantileValue

(ContourIntO2 <- ggplot(na.omit(HyperChlPlotInt), aes(Photoperiod, Par_ue, z = fit, fill = fit)) + geom_tile() +
    scale_fill_gradientn(name = bquote("µ ("~ d^-1~")"), colours=c(low = "white", intermediate = "steelblue1", high = "royalblue4"), limits  = range(minMu, maxMu), na.value = "white") +
    metR::geom_contour2(aes(label = stat(level)),
                        breaks = ContourLines,
                        skip = 0) +
    scale_x_continuous(limits = c(4, 16), breaks = c(4, 8, 12, 16)) +
    scale_y_continuous(limits = c(10, 200)) +
    xlab(NULL)+
      ylab(NULL)+
  theme_classic() +
   theme(axis.text=element_text(size=15),
          axis.title.x = element_text(size=20),
           axis.title.y = element_text(size=35)))

@@

p3_Blue <- grid.arrange(
                         ContourLowO2 + labs(title = bquote("F.   " ~ .(GamStrain) ~ '  2.5 µM' ~ "[" ~ O[2]~ "]"), size = 25) +
                           theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),
                        ContourIntO2 +  labs(title = bquote("E.   " ~ .(GamStrain) ~ '  25 µM' ~ "[" ~ O[2]~ "]"), size = 25) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()), 
                        ContourHighO2 + labs(title = bquote("D.   " ~ .(GamStrain) ~ '  250 µM' ~ "[" ~ O[2]~ "]")) + 
                          theme(legend.position = 'none', axis.title.y = element_blank(), axis.text.y = element_blank()),                          
                        legend1,    
                        legend2, 
                        legend3, 
                        layout_matrix = LayoutNiche)  
```

```{r combine red and blue light MIT9313GAM plots}

# common x-axis title
x.grob <- textGrob("Photoperiod (h)", 
                   gp = gpar(fontsize = 20))

# common y-axis title
y.grob <- textGrob("PAR (µmol photons"~ m^-2~ ~s^-1~ ")", 
                   gp = gpar(fontface="bold", fontsize = 20), rot = 90)
